Sustainable computational science:\\ the ReScience initiative

### 2017-07-11 draft.tex
Added failure to replicate case

\twocolumn[
\maketitle
\begin{small}
  \noindent
  \textbf{} \par
  \textbf{Keywords:} Open Science, Computational Science,
                     Reproducibility, Replicability, Journal, Publication
\end{small}
\vspace{10mm}
]

\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-replicability are as diverse as the domains in which it occurs.
In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences \citep{iqbal:2016},
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor.
The same remarks were recently issued for chemistry \citep{coudert:2017}.
Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the fact they rely on code and data rather than on experimental observations, which should make them immune to the aforementioned problems.\\

@@

Each submission is considered by a member of the editorial board, who
may decide to reject the submission if it does not respect the formal
publication criteria of ReScience. A submission must contain
\begin{itemize}
\item a precise reference to the work being replicated,
\item an explanation of why the authors think they have replicated the paper
      (same figures, same graphics, same behavior, etc.),
\item a description of any difficulties encountered during the
      replication,
\item open-source code that produces the replication results,
\item an explanation of this code for human readers.
\end{itemize}
A complete submission therefore consists of both computer code and an
accompanying article, which are sent to ReScience in the form of a pull
request (the process used on GitHub to submit a proposed modification
to a software project).
%
Partial replications that cover only some of the results in the
original work are acceptable, but must be justified.\\

@@

For a submission to be accepted, both reviewers must consider it
reproducible and a valid replication of the original work. As we
explained earlier, this means that the reviewers
\begin{itemize}
\item are able to run the proposed implementation on their computers,
\item obtain the same results as indicated in the accompanying paper,
\item consider these results sufficiently close to the ones reported in the original paper being replicated.
\end{itemize}
%
% The review concentrates on how easy it would be for another researcher
% to run the proposed implementation. This should be viewed in light of
% the standards in the field. If a given tool/library/software is
% mainstream in a field, it is ok to use them, but if a brand new
% standalone implementation is proposed, this must not rejected on this
% criterion.

>>>>

\twocolumn[
  \maketitle
  \vspace{5mm}
  \noindent
  \textbf{Abstract.}
  If computer science offers a large set of tools for prototyping, writing,
  running, testing, validating, sharing and replicating results, computational
  science still lags behind. In the best case, authors may provide the sources
  of their research as a compressed archive and feel confident their research
  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
  explained almost 20 years ago that, an article about computational result is
  advertising, not scholarship. The actual scholarship is the full software
  environment, code and data that produced the result. The computational part
  in computational sciences implies the use of computers, operating systems,
  tools, frameworks, libraries and data. This leads to such a large number of
  combinations (taking into account the version for each component) that the
  chances to have the exact same configuration as one of your colleagues are
  nearly zero. This draws consequences in our respective computational
  approaches in order to make sure that computational research can be actually
  and faithfully replicated.
  %
  ReScience is a peer-reviewed journal that targets computational research and
  encourages the explicit replication of already published research, promoting
  new and open-source implementations in order to ensure that the original
  research is reproducible. To achieve this goal, the whole publishing chain is
  radically different from other traditional scientific journals. ReScience
  lives on GitHub where each new implementation of a computational study is
  made available together with comments, explanations and tests. Each
  submission takes the form of a pull request that is publicly reviewed and
  tested in order to guarantee that any researcher can re-use it. ReScience is
  open and collaborative by design: everything can be modified.\\
  % \begin{small}
  % \vspace{10mm}

  \textbf{Keywords:} Open Science, Computational Science,
                     Reproducibility, Replicability, Journal, Publication
  %\end{small}
  %\vspace{10mm}
  \vfill
]

\clearpage
\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-replicability are as diverse as the domains in which it occurs.
In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences \citep{iqbal:2016},
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor.
The same remarks were recently issued for chemistry \citep{coudert:2017}.
Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the fact they rely on code and data rather than on experimental observations, which should make them immune to the aforementioned problems.\\

@@

Each submission is considered by a member of the editorial board, who
may decide to reject the submission if it does not respect the formal
publication criteria of ReScience. A submission must contain
\begin{itemize}
\item a precise reference to the work being replicated,
\item an explanation of why the authors think they have replicated the paper
  (same figures, same graphics, same behavior, etc.) or why they have failed.
\item a description of any difficulties encountered during the
      replication,
\item open-source code that produces the replication results,
\item an explanation of this code for human readers.
\end{itemize}
A complete submission therefore consists of both computer code and an
accompanying article, which are sent to ReScience in the form of a pull
request (the process used on GitHub to submit a proposed modification
to a software project).
%
Partial replications that cover only some of the results in the
original work are acceptable, but must be justified.\\

@@

For a successful submission (i.e. partial or full replication) to be accepted,
both reviewers must consider it reproducible and a valid replication of the
original work. As we explained earlier, this means that the reviewers
\begin{itemize}
\item are able to run the proposed implementation on their computers,
\item obtain the same results as indicated in the accompanying paper,
\item consider these results sufficiently close to the ones reported in the
  original paper being replicated.
\end{itemize}

For a failure to replicate submission to be accepted, we require extra steps.
to be taken. In addition to scrutiny of the submission by reviewers and
editors, we will try to contact the authors of the original research, and issue
a challenge to the community to spot and report errors in the new implementation.
If no errors are found, the submission will be accepted and the original
research will be declared non-replicable.

%
% The review concentrates on how easy it would be for another researcher
% to run the proposed implementation. This should be viewed in light of
% the standards in the field. If a given tool/library/software is
% mainstream in a field, it is ok to use them, but if a brand new
% standalone implementation is proposed, this must not rejected on this
% criterion.
